Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
tor→Tor in one more place.
The distinction between little-t tor and big-T Tor is potentially
confusing here.

Figure~\ref{fig:browser-architecture} shows the interaction of components
on the user's computer.
Rather than starting \meekclient\ as a pluggable transport directly, the tor
process starts a helper process that starts both \meekclient\
and a headless browser instance.
The headless browser runs our extension in a separate
process and separate browser profile from the browser the
user interacts with; the two browser instances share no state.
\meekclient\ is configured to issue its requests through the browser extension;
in this configuration, the headless browser is the only thing that ever touches the network.
When run with a browser extension, meek has the same TLS signature
as Firefox (Figure~\ref{fig:ciphersuites:firefox}) or
Chrome (Figure~\ref{fig:ciphersuites:chrome}).

>>>>

Figure~\ref{fig:browser-architecture} shows the interaction of components
on the user's computer.
Rather than starting \meekclient\ as a pluggable transport directly, the Tor
process starts a helper process that starts both \meekclient\
and a headless browser instance.
The headless browser runs our extension in a separate
process and separate browser profile from the browser the
user interacts with; the two browser instances share no state.
\meekclient\ is configured to issue its requests through the browser extension;
in this configuration, the headless browser is the only thing that ever touches the network.
When run with a browser extension, meek has the same TLS signature
as Firefox (Figure~\ref{fig:ciphersuites:firefox}) or
Chrome (Figure~\ref{fig:ciphersuites:chrome}).
